Closing the gap between statistical and scientific workflows for improved forecasts in ecology

### 2025-03-25 forecastflows_outline.tex
small tweaks on outline

\def\labelitemi{--}
\parindent=0pt

@@

\item Ecology super challenged to predict stuff for decision making (kind of a whole new world of relevance?)
$leftarrow$ Example of stuff to predict: populations, policy-relevant questions...

@@

\item machine learning! If we do nothing, ML $>$ process-based without question, and ML $>$ trends without mechanisms

@@

\item prediction: being aware of what is a parameter, and [mention uncertainty propagation]

>>>>

@@

\item Ecology super challenged to predict stuff for decision making (kind of a whole new world of relevance?)\\
$\rightarrow$ Example of stuff to predict: populations, policy-relevant questions...

@@

\item machine learning! If we do nothing, what's the point of not doing ML? ML $>$ process-based without question, and ML $>$ trends without mechanisms

@@

\item estimation: being aware of what is a parameter, and mention uncertainty propagation
